### 2022-02-24 ehoh/ehoh.tex
more

The main challenges we faced concerned the
representation of types and terms
(Sect.~\ref{sec:ehoh:types-and-terms}), the unification
\confrep{algorithm}{and matching algorithms}
(Sect.~\ref{sec:ehoh:unif-match}), and the indexing data structures
(Sect.~\ref{sec:ehoh:indexing}). We also adapted the
inference rules (Sect.~\ref{sec:ehoh:inferences})\confrep{ and}{,} the
heuristics (Sect.~\ref{sec:ehoh:heuristics})\confrep{}{, and the
  preprocessor (Sect.~\ref{sec:ehoh:preprocessing})}.

@@

\noindent
\begin{tabular}{ll}
  \textsf{Decompose} & $ (\cst{f} \; \tuple{s}{m} \MATCH \cst{f} \; \tuple{t}{m} \mathrel{\cdot} \overline{c}, \, \sigma) \Matchiiarrow {} ( (s_1 \MATCH t_1, \ldots, s_m \MATCH t_m) \cdot \overline{c}, \sigma ) $ \\[\jot]
  \textsf{DecomposeX} & $(x \; \tuple{s}{{m}} \MATCH u \; \tuple{t}{{m}} \mathrel{\cdot} \overline{c}, \, \sigma) \Matchiiarrow {} ( (s_1 \MATCH t_1, \ldots, s_m \MATCH t_m) \cdot \overline{c}, \sigma[x \mapsto u] )$ \\
                    & if $x$ and $u$ have the same type and either $\sigma(x)$ is undefined or $\sigma(x)=u$ \\[\jot]
  \textsf{Success} & $ ([\,], \, \sigma) \Matchiiarrow  \sigma $ \\[\jot]
  \textsf{Clash}    & $ (\cst{f} \; \tuple{s}{m} \MATCH \cst{g} \; \tuple{t}{n} \mathrel{\cdot} \overline{c}, \, \sigma) \Matchiiarrow \bot $ \\[\jot]
  \textsf{ClashTypeX}    & $(x \; \tuple{s}{{m}} \MATCH u \; \tuple{t}{{m}} \mathrel{\cdot} \overline{c}, \, \sigma) \Matchiiarrow \bot$ \\
                         & if~$x$ and $u$ have different types  \\[\jot]
  \textsf{ClashLenXF}    & $(x \; \tuple{s}{{m}} \MATCH \cst{f} \; \tuple{t}{{n}} \mathrel{\cdot} \overline{c}, \, \sigma) \Matchiiarrow \bot$ \\
                         & if~$m > n$  \\[\jot]
  \textsf{ClashLenXY}    & $(x \; \tuple{s}{{m}} \MATCH y \; \tuple{t}{{n}} \mathrel{\cdot} \overline{c}, \, \sigma) \Matchiiarrow \bot$ \\
                         & if~$x \neq y$ and $m > n$ \\[\jot]
  \textsf{ClashFX}    & $(\cst{f} \; \overline{s} \MATCH x \; \overline{t}  \mathrel{\cdot} \overline{c}, \, \sigma) \Matchiiarrow \bot$ \\[\jot]
  \textsf{Double}    & $(x \; \tuple{s}{{m}} \MATCH u \; \tuple{t}{{m}}  \mathrel{\cdot} \overline{c}, \, \sigma) \Matchiiarrow \bot$ \\
                     & if $x$ and $u$ have the same type, $\sigma(x)$ is defined, and $\sigma(x) \neq u$ \\[\jot]
\end{tabular}

\newcommand\AlphaMatch[1]{\alpha(#1)}

We need an auxiliary function to convert $\Matchiiarrow$ states to
$\Matcharrow$ states.
Let
$\AlphaMatch{\{ x_1 \mapsto s_1,\allowbreak \ldots, x_m \mapsto s_m \}}
 = \{ x_1 \MATCH s_1,\ldots,\,\allowbreak x_m \MATCH s_m \}$,
$\AlphaMatch{\overline{c}, \sigma} =
\{ c \mid c \in \overline{c} \} \mathrel\cup \AlphaMatch{\sigma}$, and
$\AlphaMatch{\bot} = \bot$.
%
Moreover, let $\mathcal{S}$ range over states of the form $(\overline{c}, \sigma)$ and
$\mathcalx{R}$ additionally range over special states of the form $\sigma$ or
$\bot$.

>>>>

The main challenges we faced involved the
representation of types and terms
(Sect.~\ref{sec:ehoh:types-and-terms}), the unification
\confrep{algorithm}{and matching algorithms}
(Sect.~\ref{sec:ehoh:unif-match}), and the indexing data structures
(Sect. \ref{sec:ehoh:indexing}). We also adapted the
inference rules (Sect.~\ref{sec:ehoh:inferences})\confrep{ and}{,} the
heuristics (Sect.~\ref{sec:ehoh:heuristics})\confrep{}{, and the
  preprocessor (Sect. \ref{sec:ehoh:preprocessing})}.

@@

\vskip\abovedisplayskip
\noindent
\begin{tabular}{ll}
  \textsf{Decompose} & $ (\cst{f} \; \tuple{s}{m} \MATCH \cst{f} \; \tuple{t}{m} \mathrel{\cdot} \overline{c}, \, \sigma) \Matchiiarrow {} ( (s_1 \MATCH t_1, \ldots, s_m \MATCH t_m) \cdot \overline{c}, \sigma ) $ \\[\jot]
  \textsf{DecomposeX} & $(x \; \tuple{s}{{m}} \MATCH u \; \tuple{t}{{m}} \mathrel{\cdot} \overline{c}, \, \sigma) \Matchiiarrow {} ( (s_1 \MATCH t_1, \ldots, s_m \MATCH t_m) \cdot \overline{c}, \sigma[x \mapsto u] )$ \\
                    & if $x$ and $u$ have the same type and either $\sigma(x)$ is undefined or $\sigma(x)=u$ \\[\jot]
  \textsf{Success} & $ ([\,], \, \sigma) \Matchiiarrow  \sigma $ \\[\jot]
  \textsf{Clash}    & $ (\cst{f} \; \tuple{s}{m} \MATCH \cst{g} \; \tuple{t}{n} \mathrel{\cdot} \overline{c}, \, \sigma) \Matchiiarrow \bot $ \\[\jot]
  \textsf{ClashTypeX}    & $(x \; \tuple{s}{{m}} \MATCH u \; \tuple{t}{{m}} \mathrel{\cdot} \overline{c}, \, \sigma) \Matchiiarrow \bot$ \\
                         & if~$x$ and $u$ have different types  \\[\jot]
  \textsf{ClashLenXF}    & $(x \; \tuple{s}{{m}} \MATCH \cst{f} \; \tuple{t}{{n}} \mathrel{\cdot} \overline{c}, \, \sigma) \Matchiiarrow \bot$ \\
                         & if~$m > n$  \\[\jot]
  \textsf{ClashLenXY}    & $(x \; \tuple{s}{{m}} \MATCH y \; \tuple{t}{{n}} \mathrel{\cdot} \overline{c}, \, \sigma) \Matchiiarrow \bot$ \\
                         & if~$x \neq y$ and $m > n$ \\[\jot]
  \textsf{ClashFX}    & $(\cst{f} \; \overline{s} \MATCH x \; \overline{t}  \mathrel{\cdot} \overline{c}, \, \sigma) \Matchiiarrow \bot$ \\[\jot]
  \textsf{Double}    & $(x \; \tuple{s}{{m}} \MATCH u \; \tuple{t}{{m}}  \mathrel{\cdot} \overline{c}, \, \sigma) \Matchiiarrow \bot$ \\
                     & if $x$ and $u$ have the same type, $\sigma(x)$ is defined, and $\sigma(x) \neq u$ \\[\jot]
\end{tabular}
\vskip\belowdisplayskip
\newcommand\AlphaMatch[1]{\alpha(#1)}
We need an auxiliary function to convert $\Matchiiarrow$ states to
$\Matcharrow$ states.
Let
$\AlphaMatch{\{ x_1 \mapsto s_1,\allowbreak \ldots, x_m \mapsto s_m \}}
 = \{ x_1 \MATCH s_1,\ldots,\,\allowbreak x_m \MATCH s_m \}$,
$\AlphaMatch{\overline{c}, \sigma} =
\{ c \mid c \in \overline{c} \} \mathrel\cup \AlphaMatch{\sigma}$, and
$\AlphaMatch{\bot} = \bot$.
%
Moreover, let $\mathcal{S}$ range over states of the form $(\overline{c}, \sigma)$ and
$\mathcalx{R}$ additionally range over special states of the form $\sigma$ or
$\bot$.
